Formalized Linear Programming

### 2019-09-23 TeX/paper.tex
Push draft of abstract

\begin{document}
\bibliographystyle{plain}
\lstset{language=lean}
\lstset{basicstyle=\normalsize}
\maketitle
\begin{abstract}
% What is the general topic we look at?
Sentence about applications of simplex.

% What is the specific research problem we face?
Most simplex solvers are non-verified implementations and are not guaranteed to be correct.i

% Why has nobody else adequately answered the research problem yet?
They are usually written in languages like C++ which are difficult to certify.
One verified implementation exists, but it is not intended to be executable in
practice.

% What is our key idea to address the stated research problem?
We implement a formally verified executable simplex solver in the Lean theorem
prover.

% What are the key steps needed to successfully implement our idea?
Our implementation uses Bland's rule to select a pivot, and a pivot
function stated without any matrix multiplication in contrast to some book
proofs on the simplex algorithm.

% What is the outcome of our work?

% What is the key global impact we envision our research to have?
This research demonstrates the practicality of Lean as a language for fast
verified algorithms.

>>>>

\begin{document}
\bibliographystyle{plain}
\lstset{language=lean}
\lstset{basicstyle=\normalsize}
\maketitle
\begin{abstract}
% What is the general topic we look at?
Correct and efficient linear programming, using the simplex
algorithm, is of high importance not only in the context of
operational research but also in programming language analysis.
% What is the specific research problem we face?
While existing solvers are robust, the lack of formally verified
implementations prevents their use in computational proofs and
rare corner-case bugs make the use of linear programming for
automatic program generation difficult.
% Why has nobody else adequately answered the research problem yet?
Today, existing implementations are either written in low-level
high-performance languages (e.g., C++), which are hard to verify, or
focus on the verification aspects but are not intended to be executable in practice.
% What is our key idea to address the stated research problem?
We address this problem by implementing an executable and verified
simplex solver in the Lean programming language.
% What are the key steps needed to successfully implement our idea?
We ensure both ease of verification and reasonable execution
performance by uses Bland's rule to select a pivot and by stating our
pivot function without large and costly matrix multiplications as
they are often used in textbook formalizations.
% What is the key global impact we envision our research to have?
Our research provides core foundations for verified linear
programming and demonstrates the practicality of Lean as a language
for fast verified constraint programming.
